---
title: "Network Data Homework 5"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Part A
# Introduction
For the part A, we are going to fit the ERGMs model. For the ERGMs model, also called exponentialdom graph models.This is a statistical models of the network.This is a very useful, flexible and powerful modeling approach for building and testing statistical models of networks. In order to construct the ERGMs model, we use the dataset of "coevolve". 

## Model 1
From the model 1, we cahnge the network to an undirected one. And to make sure the result is the same, we set a seed =123. The n we have the result for change one. 
```{r cars,echo=FALSE}
library(statnet)
library(intergraph)
library("UserNetR")
library(igraph)
data(Coevolve)
fr_w1 <- Coevolve$fr_w1
fr_w2 <- Coevolve$fr_w2
fr_w3 <- Coevolve$fr_w3
fr_w4 <- Coevolve$fr_w4
m1<- asNetwork(as.undirected(fr_w1))
m2<- asNetwork(as.undirected(fr_w2))
m3<- asNetwork(as.undirected(fr_w3))
m4<- asNetwork(as.undirected(fr_w4))
fit1 <- ergm(m1 ~ edges,control=control.ergm(seed=123))
summary(fit1)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
